A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker

### 2020-05-13 manuscript.Rmd
restored lost paragraph on dynamic document generation (commit: 3e5cf89ff21253ac91bcec554d806645456e3231)

>>>>

The translation of computational results into a human-readable summary, for example into a technical report, a presentation, or a journal manuscript, is time-consuming and error-prone. Typical errors result from copy\&paste mistakes, erroneous rounding, or missed updates of the manuscript when the computer code has changed. In order to not only create fully reproducible results but also fully reproducible reports, one needs to resort to the Literate Programming paradigm [@knuth1984literate], in which human-readable language and computer code are intermingled to create dynamic documents whose order follows the logic of thought rather then the order of the computer. R Markdown is a simple markup language to create dynamic documents with embedded chunks of R code that can be exported to standard formats such as documents (docx, rtf, epub), presentations (ppt, html) or websites (html) using the `knitr` package [@xie2015; @xie2019]. Several packages extend the functionality of knitr. Of particular note are the `papaja` package [@papaja2018], which offers additional functions to enable American Psychological Association (APA) style document formatting, including a journal-style final typeset format, and the `stargazer` package [@stargazer2018], which provides journal-ready tables and reports of statistical models.  Figure \@ref{fig:source-rmarkdown} illustrates R Markdown syntax using the `papaja` package and Figure \@ref{fig:rendered-result} shows the resulting rendered document.
